Generative Adversarial Networks

### 2017-12-02 cs6735/project/draft.tex
finished semisupervised section

\subsection{Inference GANs}
The first GAN architectures lacked the ability to map an sample $\bm{x}$ to the associated latent vector $\bm{z}$. This feature of GANs is often referred to as an inference mechanism \citep{2017arXiv171007035C}. In 2016, two new architecture were independently proposed which introduce an adversarial learned inference by proposing the addition of another generator network \citep{2016arXiv160509782D, 2016arXiv160600704D}. The paper by Dumoulin \textit{et al.} proposes a network which learns the mapping of $\bm{x}$ to $\bm{z}$ and generates a set of continuous variables. For example, if the vector $\bm{z}$ is of length $n$, then $n$ means and $n$ variances will be generated. This allows for a probability distribution for each value of $\bm{z}$. Furthermore, the discriminator is now trained upon both a sample $\bm{x}$ and latent space vector $\bm{z}$ and has to discriminate between a real and fake pairs. The reconstructed images remain of poor quality \citep{2017arXiv171007035C}.

@@

\begin{figure}
\centering
\includegraphics[scale=0.45]{progrssive_growing}
\caption{The training process of progressively growing generative adversarial networks recently introduced by Karras \texit{et al.} \citep{2017arXiv171010196K}. The generator and discriminator begin at $4x4$ resolution and progressively grow generate and discriminate $1024x1024$ resolution images.}
\label{fig:CumulativeNumberofGANPapersbyMonth}
\end{figure}

\section{Latent Space}
\section{Applications}
GANs are an exciting idea that are currently leading the frontier of deep generative models.

\subsection{Semi-Supervised Learning} \label{sec:semisupervised}
\subsection{Image Generation}
\subsection{Image to Image Translation} \label{sec:img2img}
\subsection{Super Resolution}

\section{Research Frontiers}
Evaluation, instability, mode collapse
\subsection{Divergence Measures}
\subsection{Image Quality}
\subsection{Reinforcement Learning}
Reinforcement learning

>>>>

\subsection{Inference GANs} \label{sec:inferencegan}
The first GAN architectures lacked the ability to map an sample $\bm{x}$ to the associated latent vector $\bm{z}$. This feature of GANs is often referred to as an inference mechanism \citep{2017arXiv171007035C}. In 2016, two new architecture were independently proposed which introduce an adversarial learned inference by proposing the addition of another generator network \citep{2016arXiv160509782D, 2016arXiv160600704D}. The paper by Dumoulin \textit{et al.} proposes a new generator network, referred to as an encoder, which learns the mapping of $\bm{x}$ to $\bm{z}$ and generates a set of continuous variables. For example, if the vector $\bm{z}$ is of length $n$, then $n$ means and $n$ variances will be generated. This allows for a probability distribution for each value of $\bm{z}$. Furthermore, the discriminator is now trained upon both a sample $\bm{x}$ and latent space vector $\bm{z}$ and has to discriminate between a real and fake pairs. The reconstructed images remain of poor quality \citep{2017arXiv171007035C}.

@@

\begin{figure}
\centering
\includegraphics[scale=0.45]{progressive_growing}
\caption{The training process of progressively growing generative adversarial networks recently introduced by Karras \texit{et al.} \citep{2017arXiv171010196K}. The generator and discriminator begin at $4x4$ resolution and progressively grow generate and discriminate $1024x1024$ resolution images.}
\label{fig:ProgressiveGrowingGAN}
\end{figure}

\section{Latent Space}
\section{Applications}
Although GANs are a relatively new topic, many different applications have been discovered since their inception. Several of the reoccurring themes are elaborated within this section.

\subsection{Semi-Supervised Learning} \label{sec:semisupervised}
There exist several methods for training a classifier using a GAN. These methods all take advantage of the unsupervised aspect of GANs to implement semi-supervised learning and offer a quantitative method to rank different GAN models. One general transfer learning technique involves the use of discriminator within classification tasks as a feature extractor. A new machine learning model, such as a SVM, is subsequently able to be trained on the extracted features of some layer $l$ of the discriminator. Another transfer learning approach makes use of the inference GANs mentioned in section \ref{sec:inferencegan}. Another machine learning model is trained on the last three hidden layers of the of the encoder. These techniques have both received state-of-the-art classification results \citep{2017arXiv171007035C}.

Another general approach to semi-supervised learning transforms the discriminator into a classifier of $k + 1$ classes where $k$ is the amount of real object classes. In this format, the $k + 1$ class is associated with a fake image. When a real image is given to the discriminator, it attempts to classify the sample as one of the k classes; however, when a generated or unlabeled image is given, the probabilities of the k classes are summed together to represent the probability of the image being real. Typical supervised models need more than $50,000$ labels whereas state of the art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ in size \citep{2017arXiv170100160G}.

\subsection{Image Generation}
\subsection{Image to Image Translation} \label{sec:img2img}
\subsection{Super Resolution}
\subsection{Reinforcement Learning}
Reinforcement learning
